Yeast Tandem Deamination Figure Generation

### 2022-06-16 R/ArabidopsisDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Various tweaks, bugfixes, and additional filtering

>>>>

```{r CPD_sequence_frequencies_filtered, fig.width = 11, fig.height = 8}
min5PrimeCutSiteDistance = 15
max5PrimeCutSiteDistance = 25
for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]],
                          title = paste(c("CPD", titleCaseFiltering,
                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
                          minReadLength = min5PrimeCutSiteDistance, maxReadLength = max5PrimeCutSiteDistance)
}
```

```{r CPD_sequence_frequencies_filtered_x2, fig.width = 5, fig.height = 8}
min5PrimeCutSiteDistance = 15
max5PrimeCutSiteDistance = 25
for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]]$ZT2,
                          title = paste(c("CPD", titleCaseFiltering,
                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
                          minReadLength = min5PrimeCutSiteDistance, maxReadLength = max5PrimeCutSiteDistance)
}
```

### 2022-06-16 R/ArabidopsisDeaminationSequenceAndPositionFigureGeneration.rmd
Various tweaks, bugfixes, and additional filtering

>>>>

```{r CPD_mismatch_position_frequencies_by_read_length_filtered, fig.width = 5, fig.height = 5}
for (i in seq_along(CPDMismatchData)) {
  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["ZT2"], includedTypes = c("C>T"),
                                           title = paste(c("CPD", titleCaseFiltering,
                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
                                           zScoreTables = CPDMMFreqZScores[[i]])
  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["ZT2"], includedTypes = c("C>T"),
                                           title = paste(c("CPD", titleCaseFiltering,
                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
                                           zScoreTables = CPDMMFreqZScores[[i]], posType = FIVE_PRIME)
}
```

### 2022-06-16 R/ArabidopsisTandemDeaminationFigureGeneration.rmd
Various tweaks, bugfixes, and additional filtering

>>>>

```{r CPD_mismatch_position_frequencies_by_read_length_filtered, fig.width = 5, fig.height = 5}
for (i in seq_along(CPDMismatchData)) {
  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["ZT2"],
                                           title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
                                                           "Mismatch Pos Freq", repNames[i]),
                                                         collapse = ' '),
                                           zScoreTables = CPDMMFreqZScores[[i]])
  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["ZT2"], posType = FIVE_PRIME,
                                           title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
                                                           "Mismatch Pos Freq", repNames[i]),
                                                         collapse = ' '),
                                           zScoreTables = CPDMMFreqZScores[[i]])
}
```

### 2022-06-16 R/CS-BDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Various tweaks, bugfixes, and additional filtering

```{r CPD_sequence_frequencies, fig.width = 11, fig.height = 9}
for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]],
                          title = paste(c("CPD", titleCaseFiltering,
                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
}

>>>>

```{r CPD_sequence_frequencies, fig.width = 11, fig.height = 9}
for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]],
                          title = paste(c("CPD", titleCaseFiltering,
                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
}

### 2022-06-16 R/NHF1DeaminationAnchoredExcisionSiteFigureGeneration.rmd
Various tweaks, bugfixes, and additional filtering

```{r CPD_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
min5PrimeCutSiteDistance = 13
max5PrimeCutSiteDistance = 25

@@

```{r CPD_mismatch_anchored_purine_frequencies_x2, fig.width = 5, fig.height = 9}
min5PrimeCutSiteDistance = 13
max5PrimeCutSiteDistance = 25

@@

```{r CPD_sequence_frequencies_filtered, fig.width = 11, fig.height = 8}
min5PrimeCutSiteDistance = 13
max5PrimeCutSiteDistance = 25
for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]],
                          title = paste(c("CPD", titleCaseFiltering,
                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
                          minReadLength = min5PrimeCutSiteDistance,
                          max5PrimeCutSiteDistance = max5PrimeCutSiteDistance)
}
```

```{r CPD_sequence_frequencies_filtered_x2, fig.width = 5, fig.height = 8}
min5PrimeCutSiteDistance = 13
max5PrimeCutSiteDistance = 25
for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]]$`1h`,
                          title = paste(c("CPD", titleCaseFiltering,
                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
                          minReadLength = min5PrimeCutSiteDistance,
                          max5PrimeCutSiteDistance = max5PrimeCutSiteDistance)
}
```

>>>>

```{r CPD_mismatch_anchored_purine_frequencies_filtered, fig.width = 11, fig.height = 9}
min5PrimeCutSiteDistance = 13
max5PrimeCutSiteDistance = 25

@@

```{r CPD_mismatch_anchored_purine_frequencies_filtered_x2, fig.width = 5, fig.height = 9}
min5PrimeCutSiteDistance = 13
max5PrimeCutSiteDistance = 25

@@

```{r CPD_sequence_frequencies_filtered, fig.width = 11, fig.height = 8}
min5PrimeCutSiteDistance = 13
max5PrimeCutSiteDistance = 25
for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]],
                          title = paste(c("CPD", titleCaseFiltering,
                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
                          minReadLength = min5PrimeCutSiteDistance, maxReadLength = max5PrimeCutSiteDistance)
}
```

```{r CPD_sequence_frequencies_filtered_x2, fig.width = 5, fig.height = 8}
min5PrimeCutSiteDistance = 13
max5PrimeCutSiteDistance = 25
for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]]$`1h`,
                          title = paste(c("CPD", titleCaseFiltering,
                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
                          minReadLength = min5PrimeCutSiteDistance, maxReadLength = max5PrimeCutSiteDistance)
}
```

### 2022-06-16 R/NHF1DeaminationSequenceAndPositionFigureGeneration.rmd
Various tweaks, bugfixes, and additional filtering

>>>>

```{r CPD_mismatch_position_frequencies_by_read_length_filtered, fig.width = 5, fig.height = 5}
for (i in seq_along(CPDMismatchData)) {
  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["1h"], includedTypes = c("C>T"),
                                           title = paste(c("CPD", titleCaseFiltering,
                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
                                           zScoreTables = CPDMMFreqZScores[[i]])
  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["1h"], includedTypes = c("C>T"), posType = FIVE_PRIME,
                                           title = paste(c("CPD", titleCaseFiltering,
                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
                                           zScoreTables = CPDMMFreqZScores[[i]])
}
```

### 2022-06-16 R/NHF1TandemDeaminationFigureGeneration.rmd
NHF1 bugfixes and tweaks
Various tweaks, bugfixes, and additional filtering

>>>>

```{r CPD_mismatch_position_frequencies_by_read_length_filtered, fig.width = 5, fig.height = 5}
for (i in seq_along(CPDMismatchData)) {
  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["1h"],
                                           title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
                                                           "Mismatch Pos Freq", repNames[i]),
                                                         collapse = ' '),
                                           zScoreTables = CPDMMFreqZScores[[i]])
  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["1h"], posType = FIVE_PRIME,
                                           title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
                                                           "Mismatch Pos Freq", repNames[i]),
                                                         collapse = ' '),
                                           zScoreTables = CPDMMFreqZScores[[i]])
}
```

### 2022-06-16 R/YeastDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Various tweaks, bugfixes, and additional filtering

>>>>

```{r CPD_sequence_frequencies_filtered, fig.width = 11, fig.height = 8}
min5PrimeCutSiteDistance = 11
max5PrimeCutSiteDistance = 19
for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]],
                          title = paste(c("CPD", titleCaseFiltering,
                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
                          minReadLength = min5PrimeCutSiteDistance, maxReadLength = max5PrimeCutSiteDistance)
}
```

```{r CPD_sequence_frequencies_filtered_x2, fig.width = 5, fig.height = 8}
min5PrimeCutSiteDistance = 11
max5PrimeCutSiteDistance = 19
for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]]$`20min`,
                          title = paste(c("CPD", titleCaseFiltering,
                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
                          minReadLength = min5PrimeCutSiteDistance, maxReadLength = max5PrimeCutSiteDistance)
}
```

### 2022-06-16 R/YeastDeaminationSequenceAndPositionFigureGeneration.rmd
Various tweaks, bugfixes, and additional filtering

>>>>

```{r CPD_mismatch_position_frequencies_by_read_length_filtered, fig.width = 5, fig.height = 5}
for (i in seq_along(CPDMismatchData)) {
  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["20min"], includedTypes = c("C>T"),
                                           title = paste(c("CPD", titleCaseFiltering,
                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
                                           zScoreTables = CPDMMFreqZScores[[i]])
  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["20min"], includedTypes = c("C>T"),
                                           title = paste(c("CPD", titleCaseFiltering,
                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
                                           zScoreTables = CPDMMFreqZScores[[i]], posType = FIVE_PRIME)
}
```

### 2022-06-16 R/YeastTandemDeaminationFigureGeneration.rmd
Various tweaks, bugfixes, and additional filtering

>>>>

```{r CPD_mismatch_position_frequencies_by_read_length_filtered, fig.width = 5, fig.height = 5}
for (i in seq_along(CPDMismatchData)) {
  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["20min"],
                                           title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
                                                           "Mismatch Pos Freq", repNames[i]),
                                                         collapse = ' '),
                                           zScoreTables = CPDMMFreqZScores[[i]])
  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["20min"], posType = FIVE_PRIME,
                                           title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
                                                           "Mismatch Pos Freq", repNames[i]),
                                                         collapse = ' '),
                                           zScoreTables = CPDMMFreqZScores[[i]])
}
```
